PANCHANGE_analysis

### 2021-01-13 Final_analyses_checks_notebook.Rmd
detail checks and fixes
added knitted paper detail check doc
fixed retrospective data inclusion criteria

RETROSPECTIVE
```{r subset retrospective data }
dat.retro <- alldat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
        data_group_gad == "All prepandemic, baseline and retrospective data") |
       (data_group_phq == "Baseline and retrospective data" |
          data_group_phq == "All prepandemic, baseline and retrospective data") |
       (data_group_pcl == "Baseline and retrospective data" |
          data_group_pcl == "All prepandemic, baseline and retrospective data"))
  )

@@

>>>>

RETROSPECTIVE
```{r subset retrospective data }
dat.retro <- alldat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
        data_group_gad == "All prepandemic, baseline and retrospective data") |
       (data_group_phq == "Baseline and retrospective data" |
          data_group_phq == "All prepandemic, baseline and retrospective data") |
        (data_group_pcl == "Baseline data only" |
      data_group_pcl == "All prepandemic, baseline and retrospective data"))
  )

@@

### full data (only excluding for NA on age, gender, MHD)

```{r full data n}

alldat %>%
  freq(alldat$Sample)

```
### retrospective data (excluding for NA on age, gender, MHD, or either retrospective or baseline data )
with exception of PCL which has nor etrospective data

```{r retro data n}

dat.retro %>%
  freq(Sample)

### Prepandemic data (excluding for NA on age, gender, MHD, or either prepandemic or baseline data )

```{r prepan data n}

dat.prepan %>%
  freq(Sample)

### 2021-01-13 PANCHANGE_analysis.Rmd
fixed retrospective data inclusion criteria

```{r subsample for retro-baseline analysis}
dat.retro <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data"))
  )

@@

Sensitivity analysis for individuals who signed up to GLAD (prepan) either 3, 6 or 9 months before the pendemic began.
```{r subsample for pre-pan sensitivity analysis}
# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_3months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_3_months_numeric == 1 # Only participants who signed up between December 1st 2019 and March 1st 2020
  )

# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_6months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_6_months_numeric == 1 # Only participants who signed up between September 1st 2019 and March 1st 2020
  )

# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_9months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_9_months_numeric == 1 # Only participants who signed up between June 1st 2019 and March 1st 2020
  )

>>>>

Important note::: PCL does not have retrospective data, so we allow Baseline only or All prepandemic, baseline and retrospective
```{r subsample for retro-baseline analysis}
dat.retro <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline data only" |
      data_group_pcl == "All prepandemic, baseline and retrospective data"))
  )

@@

Sensitivity analysis for individuals who signed up to GLAD (prepan) either 3, 6 or 9 months before the pendemic began.
```{r subsample for pre-pan sensitivity analysis}
# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_3months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "Baseline data only" |
      data_group_pcl == "All prepandemic, baseline and retrospective data"))  &
      prepandemic_3_months_numeric == 1 # Only participants who signed up between December 1st 2019 and March 1st 2020
  )

# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_6months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "Baseline data only" |
      data_group_pcl == "All prepandemic, baseline and retrospective data")) &
      prepandemic_6_months_numeric == 1 # Only participants who signed up between September 1st 2019 and March 1st 2020
  )

# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_9months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "Baseline data only" |
      data_group_pcl == "All prepandemic, baseline and retrospective data"))  &
      prepandemic_9_months_numeric == 1 # Only participants who signed up between June 1st 2019 and March 1st 2020
  )
